Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-07-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 3 and 4
Continued to revise chapters based on CF comments.

Figures~\ref{HF_Center_TWNG_comp} and \ref{HF_Edge_TWNG_comp} provide the heat flux measurements for the two vertical arrays of gauges positioned along the centerline and the edge of the natural gas burner.  The series of graphs show that the peak heat flux increases by as the burner is moved toward the wall. One exception is when the burner was moved from the 0.15~m position to the 0.0~m from the wall. In this comparison the peak heat flux values for the gauges located above the edge of the burner do not uniformly increase.  In fact the peak heat flux actually decreased as the burner was moved from the 0.15~m position to the 0.0~m position. This decrease was due to the change in view angle between the flame closest to the burner and the lower heat flux gauges at the edge of the burner.

@@

Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels. Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner was moved away from the wall. The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown. Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m. As with the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.  A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.

@@

\section{Experimental Arrangement}
This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface. These experiments were conducted in a similar manner as the non-combustible instrumented wall experiments, the only new variable is the painted, gypsum wallboard. These experiments enable us to examine our ignition/no ignition predictions from the previous experiments.  A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the experiments in the study.

>>>>

Figures~\ref{HF_Center_TWNG_comp} and \ref{HF_Edge_TWNG_comp} provide the heat flux measurements for the two vertical arrays of gauges positioned along the centerline and the edge of the natural gas burner.  The series of graphs show that the peak heat flux increases as the burner is moved toward the wall. One exception is when the burner was moved from the 0.15~m position to the 0.0~m from the wall. In this comparison the peak heat flux values for the gauges located above the edge of the burner do not uniformly increase.  In fact the peak heat flux actually decreased as the burner was moved from the 0.15~m position to the 0.0~m position. This decrease was due to the change in view angle between the flame closest to the burner and the lower heat flux gauges at the edge of the burner.

@@

Figure~\ref{NCTW_Surf_Center_comp} shows the wall temperatures based on the array of thermocouples installed in the wall and position along the vertical centerline of the burners for each of the three fuels. Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner increased from the wall. The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown. Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m. As with the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.  A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.

@@

\section{Experimental Arrangement}
This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface. These experiments were conducted in a similar manner as the non-combustible instrumented wall experiments, the only new variable is the painted, gypsum wallboard. These experiments enabled the examination of the ignition/no ignition predictions from the previous experiments.  A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the experiments in the study.
